MSB1015_Assignment 2

### 2019-09-28 MSB1015_Assignment2_SuzannetenHage.Rmd
Update MSB1015_Assignment2_SuzannetenHage.Rmd
Added two more descriptors to make predictions more precise. 
Added an error  vs. number of components plot.

#Reformatting of smiles into correct format for CDK. Kekulise checks for electrons, and prevents parsing of incorrect smiles. 
parsed_smiles <- parse.smiles(data_raw$smiles, kekulise=TRUE)
#Determine which descriptors to get. 
descNames <- c(
'org.openscience.cdk.qsar.descriptors.molecular.APolDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.WienerNumbersDescriptor')
#Get descriptors
descriptors <- eval.desc(parsed_smiles, descNames)

@@

#Splitting data into a training and test set. 
set.seed(50) 
sample = sample.split(data, SplitRatio = percentage_test)
train = subset(data, sample == FALSE)
test  = subset(data, sample == TRUE)

@@

#Training of the PLS model. 
PLS_model <- plsr(data_raw.bp ~ (apol + WPATH + WPOL), 
                  data = train, 
                  validation = "CV"
                  )

@@

#Plot the predicted data vs. the original data. 
plot(test$data_raw.bp, predicted.bp[,,3], xlim=c(350,1000), ylim=c(350,1000))
cor(predicted.bp[,,3], test$data_raw.bp)

>>>>

#Reformatting of smiles into correct format for CDK. Kekulise checks for electrons, and prevents parsing of incorrect smiles. 
parsed_smiles <- parse.smiles(data_raw$smiles, kekulise=TRUE)

#Determine which descriptors to get. 
descNames <- c(
'org.openscience.cdk.qsar.descriptors.molecular.APolDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.WienerNumbersDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.MDEDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.FMFDescriptor'
)

#Get descriptors
descriptors <- eval.desc(parsed_smiles, descNames)

@@

#Splitting data into a training and test set. 
set.seed(101) 
sample = sample.split(data, SplitRatio = percentage_test)
train = subset(data, sample == FALSE)
test  = subset(data, sample == TRUE)

@@

#Training of the PLS model. 
PLS_model <- plsr(data_raw.bp ~  ., 
                  data = train, 
                  validation = "CV"
                  )

@@

```{r} 
#Plot the error vs. the number of components
plot(error)

#Plot the predicted data vs. the original data. 
plot(test$data_raw.bp, predicted.bp[,,10], xlim=c(350,1000), ylim=c(350,1000))

#Correlation between predicted and original test data. 
corcoef <- cor(predicted.bp[,,10], test$data_raw.bp)
